\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
"to name a few" sounds too colloquial
Mark-up should not be hyphenated

%%%%%%%%%%%%%%%%% Tessellated polygons
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the MCRT simulation.

@@

%%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
To exchange geometry descriptions between software packages the Geometry Description Mark-up Language (GDML) was developed~\cite{GDML}. 
GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
GDML format and it is commonly used as an exchange format for Geant4 geometries.

>>>>

%%%%%%%%%%%%%%%%% Tessellated polygons
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL with
more modern examples including PLY and OBJ. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the MCRT simulation.

@@

%%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
To exchange geometry descriptions between software packages the Geometry Description Markup Language (GDML) was developed~\cite{GDML}. 
GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
GDML format and it is commonly used as an exchange format for Geant4 geometries.
